## Real Estate & Mortgage Results

```{r real_estate_load_data}
real_estate_data <- jsonlite::read_json(
  path = file.path(real_estate_dir, "data", "data.json")
)[["exec_sum"]]

remove_list_null <- function(x){
  nulls <- which(sapply(x, is.null))
  if (length(nulls) > 0){
    x <- x[-nulls]
  }
  return(x)
}

convert_re_user_path <- function(
  wp_path,
  parent_dir = file.path(real_estate_dir, "img")
  ){
  filename <- basename(wp_path)
  return(file.path(parent_dir, filename))
}

real_estate_paths <- real_estate_data[["real_estate"]][[tolower(language)]]
cleaned_real_estate_paths <- real_estate_paths %>%
  remove_list_null %>%
  lapply(X = ., FUN = convert_re_user_path)
stopifnot(all(sapply(X = cleaned_real_estate_paths, FUN = file.exists)))

mortgage_paths <- real_estate_data[["mortgage"]][[tolower(language)]]
cleaned_mortgage_paths <- mortgage_paths %>%
  remove_list_null %>%
  lapply(X = ., FUN = convert_re_user_path)
stopifnot(all(sapply(X = cleaned_mortgage_paths, FUN = file.exists)))
```


### Current Status

Shares of energy sources compared to all participants 

Directly held buildings

```{r real_estate_bar_chart, out.width = '50%'}
cat(Sys.time())
knitr::include_graphics(cleaned_real_estate_paths[["png_energy_carrier"]])
```

Geographical distribution of directly held buildings by use 

```{r real_estate_map, out.width = '50%'}
knitr::include_graphics(cleaned_real_estate_paths[["png_map"]])
```

Mortgages 

```{r real_estate_mortgages_bar_chart, out.width = '50%'}
knitr::include_graphics(cleaned_mortgage_paths[["png_energy_carrier"]])
```

Link für Hinweise auf mögliche physische Klimarisiken: 

Natural Hazards [https://map.geo.admin.ch/?topic=bafu&lang=en&bgLayer=ch.swisstopo.pixelkarte-grau&catalogNodes=825,826,843,849,851,1505]

Distribution of the average CO_{2} intensity of your real estate portfolio (directly held buildings) compared to peers. 

```{r real_estate_distribution, out.width = '50%'}
knitr::include_graphics(cleaned_real_estate_paths[["png_co2_distribution"]])
```

Distribution of the mean CO_{2} intensity of your mortgage portfolio compared to peers. 

```{r mortgage_distribution, out.width = '50%'}
knitr::include_graphics(cleaned_mortgage_paths[["png_co2_distribution"]])
```

### Future Status

Reduction path of all directly held buildings with the submitted refurbishment plans. 

```{r real_estate_reduction_path, out.width = '50%'}
knitr::include_graphics(cleaned_real_estate_paths[["png_pathway"]])
```

Proportion of their mortgages that are above or below the reduction path for net zero by 2050

```{r real_estate_reduction_proportion, out.width = '50%'}
knitr::include_graphics(cleaned_mortgage_paths[["png_stranded_asset"]])
```

\newpage
